---
title: "The flagsvg package: Bringing together differnt sources of SVG flags from around the internet"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: false
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{The flagsvg package: Bringing together differnt sources of SVG flags from around the internet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
dev.off <- function(){
  invisible(grDevices::dev.off())
}
```

The `flagsvg` package provides links to SVG flag files on Github and Wikimedia to enable easy importing into R. 


## Installing `flagsvg`

On Windows or macOS the package is most easily installed via CRAN.

```r
install.packages("flagsvg")
```

## Flag Search



## Flag Databases

The data frames `github_flags` and `wikimedia_flags` are the two main features of the `flagsvg` package each contain links to SVG flag files. Both have common columns

    - `flag_url` for the url of the flag SVG file
    - `geo_level` for 
    
## Reading SVG files in to R

Given the URL or set of URLs from a subset of the `flag_url` column of either of `github_flags` and `wikimedia_flags`, files can read into R using the `image_read_svg()` function in the `magick` package (other functions also exist in R to read in SVG files).

```{r, message=FALSE, warning=FALSE, eval = require(rsvg, quietly = TRUE)}
library(flagsvg)
library(magick)
library(tidyverse)

flags_gitub %>%
  slice(1) %>%
  pull(flag_url) %>%
  image_read_svg(height = 300)
```

```{r}
flags_gitub %>%
  filter(geo_level == "maritime") %>%
  pull(flag_url) %>%
  image_read_svg(height = 300) %>%
  image_animate(optimize = TRUE, fps = 5)
```
